Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-01-30 src/tex/ms.tex
#1: edit

\citet{Ranjan2017b} speculated that UV photochemistry might be rate-limiting for abiogenesis, particularly on planets orbiting M dwarfs, due to their lower baseline UV fluxes.
This could delay abiogenesis by orders of magnitude, resulting in a continuous dependence of abiogenesis likelihood on UV flux.
However, recent studies challenge this view for the cyanosulfidic scenario.
\citet{Rimmer2021}  calculated photochemical timescales on early Earth at 180-300 hours (7.5-12.5 days), significantly shorter than the ~1000-year timescale for stochastic geological events~\citep{Rimmer2023}.
Even with 1000x slower photochemistry on M-dwarf planets, abiogenesis would occur within 20-30 years — geologically negligible compared to stochastic processes — supporting the step-function model.

>>>>

\citet{Ranjan2017b} speculated that UV photochemistry might be rate-limiting for abiogenesis, particularly on planets orbiting M dwarfs, due to their lower baseline UV fluxes.
This could delay abiogenesis by orders of magnitude, resulting in a continuous dependence of abiogenesis likelihood on UV flux.
However, recent studies challenge this view for the cyanosulfidic scenario.
\citet{Rimmer2021}  calculated photochemical timescales on early Earth at 180-300 hours (7.5-12.5 days), significantly shorter than the timescale for stochastic geological events~\citep{Rimmer2023}.
Even with 1000x slower photochemistry on M-dwarf planets, abiogenesis would occur within 20-30 years — geologically negligible compared to stochastic processes — supporting the step-function model.
